Transparency of COVID-19-related research - Analysis

### 2022-03-09 rmarkdown-covid-19-transparent-analysis.Rmd
Update rmarkdown-covid-19-transparent-analysis.Rmd
added here::here() and some code cleaning

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Documents/GitHub/covid-transparency/data')
```

@@

```{r}
pacman::p_load(dplyr,
               ggplot2,
               knitr)
```

# Loading the datasets
First, set working directory to the folder that has all the datasets in it using setwd() function and then run the following code:
```{r}
opendata <- read.csv("covid_transparency_opendata.csv")
```

@@

First, adding the real publication year and month to the datasets. The real publication year/month is the year/month the paper was first appear online stored in firstPublicationDate column.
```{r}
library(lubridate)

opendata <- opendata %>%
  mutate(year_firstpub = year(
    as.POSIXlt(firstPublicationDate, 
               format = "%Y-%m-%d")),
    month_firstpub = month(
      as.POSIXlt(firstPublicationDate, 
               format = "%Y-%m-%d")
    )
    )
```

@@

>>>>

@@

```{r}
pacman::p_load(tidyverse,
               lubridate, 
               here, 
               ggplot2,
               knitr)
```

```{r, setup, include=FALSE}
# knitr::opts_knit$set(root.dir = '~/Documents/GitHub/covid-transparency/data')
```

# Loading the datasets
First, set working directory to the folder that has all the datasets in it using setwd() function and then run the following code:
```{r}
opendata <- read.csv(here("data", "covid_transparency_opendata.csv"))
```

@@

First, adding the real publication year and month to the datasets. The real publication year/month is the year/month the paper was first appear online stored in firstPublicationDate column.
```{r}
opendata <- opendata %>%
        mutate(year_firstpub = year(as.POSIXlt(firstPublicationDate,
                                               format = "%Y-%m-%d")),
               month_firstpub = month(as.POSIXlt(firstPublicationDate,
                                                 format = "%Y-%m-%d")))
```

@@

Also, same table, but with all the journals

```{r}
opendata %>% 
        mutate(journal = fct_lump_prop(journal, prop = 0.01) ) %>% 
        count(journal) %>% 
        arrange(desc(n)) %>% 
        knitr::kable()
```
